%% -*- coding: utf-8; -*-

\documentclass[master,american]{ThesisPUC}

%---------- Math ----------%
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bbm}
%---------- Floting ----------%
\usepackage{float}
% ---------- References ----------%
%\usepackage[sort&compress,round,comma,numbers]{natbib}
%\usepackage{natbib}
%---------- Algorithm ----------%
\usepackage[algosection, algoruled]{algorithm2e}
%---------- Tables ----------%
\usepackage{multicol}
\usepackage{booktabs}
%---------- TiKz ----------%
\usepackage{threeparttable}
\usepackage{standalone}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{psfrag,epsf}
\usepackage{todonotes}
\usepackage{multirow}

\graphicspath{{images/}}

% ---------- Cover ----------%
% Adjust the advisor's title according to gender(Prof. or Prof$^{\text{a}}$.)
\author{Alexandre Marangoni Costa}
\authorR{Costa, Alexandre Marangoni}
\advisor{Marcus Vinicius Soledade Poggi de Aragão}{Prof.}
\advisorR{Poggi de Aragão, Marcus V.S.}
%\coadvisor{Simone Diniz Junqueira Barbosa}{Prof$^{\text{a}}$.}
%\coadvisorR{Barbosa, Simone Diniz Junqueira}

% This thesis will use colored figures, this goes in the catalographic sheet
\usecolour{true}
\title{Visão teórica e prática sobre a aplicação de Deep Learning na construção de agentes de pôquer}
\titleuk{Deep learning overview and application to build poker playing agents}

\day{26$^{th}$}
\month{February}
\myyear{2019}

% CDD is the registry number of the area, given by the library. Our area (informatics) is 004.
\city{Rio de Janeiro}
\CDD{004}
\department{Informática}
\program{Informática}
\school{Centro Técnico Científico}
\university{Pontifícia Universidade Católica do Rio de Janeiro}
\uni{PUC-Rio}

%---------- Jury ----------%

% Internal jury members are declared with \jurymember{name}{title}{department}{university}
% external jury members are declared with \extjurymember{name}{title}{university}
\jury{
  \jurymember{Hélio Côrtes Vieira Lopes}{Prof.}{Departamento de Informática}{PUC-Rio}
  \jurymember{Thibaut Vidal}{Prof.}{Departamento de Informática}{PUC-Rio}
  \jurymember{Bruno Feijó}{Prof.}{Departamento de Informática}{PUC-Rio}
  % The person below is mandatory.
  \schoolhead{Márcio da Silveira Carvalho}{Prof.}
}

%---------- Front letters ----------%
\resume
{
Bachelor's in Computer Engineer (2013) at the Pontifícia Universidade Católica do Rio de Janeiro (PUC-Rio). Joined the Master Program in Informatics at the Pontifical Catholic University of Rio de Janeiro (PUC-Rio) in 2017.
}

\acknowledgment
{
  \noindent
  
  To FAPERJ and CAPES, for financing this research.
  
  To Marcus Poggi, who is an advisor but also a close friend.
  
  To my family, for unconditional love.
  
  To my friends, who turn life into a beautiful journey.
  
  To Alan Turing, for making computation a reality.
  
  To God, for making everything a reality.
}


% Workaround for keywords. The keywords in the catalographic sheet must be separated by dots, while the ones shown in the abstract must be separated by semi-colons.
% Thats why we have two commands for each language: \keywords declares the keywords for the catalographic sheet, while \keywordsabstract declares the ones for the abstract.
\keywords
{
  \key{Deep Learning}
  \key{Redes Neurais}
  \key{Aprendizado de Máquina}
  \key{Pôquer}
  \key{Simulação Multiagente}
}

\keywordsabstract
{
  \key{Deep Learning;}
  \key{Redes Neurais;}
  \key{Aprendizado de Máquina;}
  \key{Pôquer;}
  \key{Simulação Multiagente;}
}

\keywordsuk
{
  \key{Deep Learning}
  \key{Neural Network}
  \key{Machine Learning}
  \key{Poker}
  \key{Multi-Agent Simulation}
}

\keywordsabstractuk
{
  \key{Deep Learning;}
  \key{Neural Network;}
  \key{Machine Learning;}
  \key{Poker;}
  \key{Multi-Agent Simulation;}
}

\abstract{
  A ciência de dados precisa de uma grande quantidade de dados para testar e melhorar soluções. Jogos são largamente usados para abstrair situações da vida real. Rodadas de pôquer são um bom exemplo pois, por não saber as cartas dos oponentes, o jogador analisa um cenário de informação incompleta numa competição de agentes que envolve conhecimento probabilístico, análise de risco e brefe. Isso o diferencia de xadrez, damas e jogos de conhecimento perfeito e algoritmos de busca em forca bruta sobre o espaço de soluções. Usar o pôquer como um caso de teste possibilita a análise de diferentes abordagens usadas na vida real, porém num cenário mais controlado. Esta dissertação propõe um arcabouço de funcionalidades para criar e testar diferentes algorítimos de Deep Learning, que podem jogar pôquer entre sí, aprender com o histórico e maximizar suas recompensas.
}

\abstractuk{
  Data science research needs real examples to test and improve solutions. Games are widely used to mimic those real-world examples. Poker rounds are a good example of imperfect information state with competing agents dealing with probabilistic knowledge, risk assessment, and possible deception, unlike chess, checkers and perfect information brute-force search style of games. By using poker as a test-bed we can analyze different approaches used in real-world examples, in a more controlled environment, which should give great insights on how to tackle those real-world scenarios. We propose a framework to build and test different neural networks that can play against each other, learn from a supervised experience and maximize its rewards.
}

\epigraph{"Hard" is everything you still don't know}
\epigraphauthor{Hamazaki, Geiza}

% WARNING
% The epigraph, if present, must come before the first chapter, always.
% There is a list of abreviations (abrevs.tex) which is included automatically in the ThesisPUC.cls, and is optional, comment the \include{abrevs} line if you do not wish to included it.
\begin{document}

\input{Introduction.tex}
\input{Background.tex}
\input{Learning.tex}
\input{Architecture.tex}
\input{Evaluation.tex}
\input{Conclusions.tex}

The remainder of this thesis is organized as follows: Chapter~\ref{chap:related-work} presents the state-of-the-art in Artificial Intelligent poker agents. Next, in Chapter~\ref{chap:background} we describe poker foundations and explain computer poker features that can help convergence of neural networks in early poker stages. Chapter~\ref{chap:learning} shows how neural networks work to gradually improve its predictions and how we used reinforcement learning to adapt the model to multi-step games. Chapter~\ref{chap:architecture} describes the project architecture, simulation, data storage, learn and predict modules. Chapter~\ref{chap:evaluation} presents details about the experiments and the associated results. Chapter~\ref{chap:conclusions} presents some concluding remarks and directions for future work.

\arial
\bibliography{references}

% Apendix chapters below.
%\normalfont
%\appendix
%\input{appendix.tex}

\end{document}